---
title: "Project of Machine Learning Course"
author: "TinocoHA"
date: "22 de noviembre de 2015"
output: html_document
---

#Abstract

Using devices such as Jawbone Up, Nike FuelBand, and Fitbit it is now possible to collect a large amount of data about personal activity relatively inexpensively. These type of devices are part of the quantified self movement – a group of enthusiasts who take measurements about themselves regularly to improve their health, to find patterns in their behavior, or because they are tech geeks. One thing that people regularly do is quantify how much of a particular activity they do, but they rarely quantify how well they do it.

## Reading and Loading Data

```{r}

# Changing the main directory
setwd("C:/Users/Tinoco/Google Drive/2. Research (Current)/(2015) Courses/(2015) Especialization in Data Science_/8. Machine Learning/Project_Machine_Learning")

# This function was recycled from another code found in internet

load <- function(pkg){
  new.pkg <- pkg[!(pkg %in% installed.packages()[, "Package"])]
  if (length(new.pkg))
    install.packages(new.pkg, dependencies = TRUE)
  sapply(pkg, require, character.only = TRUE)
} 

packages <- c("data.table", "Hmisc", "caret", "randomForest", "foreach", "doParallel", "rattle", "acepack")
load(packages)

# Loading Training and Evaluation Data

training_data <- read.csv("pml-training.csv", na.strings=c("#DIV/0!"," ", "", "NA", "NAs", "NULL"))
evaluation_data <- read.csv("pml-testing.csv", na.strings=c("#DIV/0!"," ", "", "NA", "NAs", "NULL"))

# returning common names 
train_names <- names(training_data)
test_names <- names(evaluation_data)
cross_names <- intersect(names(training_data), names(evaluation_data))
print(cross_names)

```

## Cleaning Data


```{r}
# Cleaning Data
# Removing columns from data

clean_train <- training_data[,-(1:7)]
N_index <- nearZeroVar(clean_train, saveMetrics=FALSE, freqCut=70/30)
allnames <- names(clean_train)

# Choosing columns different to N_index
Nnames <- allnames[-N_index]
clean_train <- clean_train[Nnames]

## function by Michael Szczepaniak 
## Creates a data frame with three columns: index, ColumnName and
## FractionMissing.
## index is the column index in df corresponding to ColumnName
## ColumnName is as the name implies: the name the column in df
## FractionMissing is the fraction of values that are missing or NA.
## The closer this value is to 1, the less data the column contains

getFractionMissing <- function(df = rawActitivity) {
  colCount <- ncol(df)
  returnDf <- data.frame(index=1:ncol(df),
                         columnName=rep("undefined", colCount),
                         FractionMissing=rep(-1, colCount),
                         stringsAsFactors=FALSE)
  for(i in 1:colCount) {
    colVector <- df[,i]
    missingCount <- length(which(colVector == "") * 1)
    missingCount <- missingCount + sum(is.na(colVector) * 1)
    returnDf$columnName[i] <- as.character(names(df)[i])
    returnDf$FractionMissing[i] <- missingCount / length(colVector)
  }
  
  return(returnDf)
}

percentMissingDF <- getFractionMissing(clean_train)
print(percentMissingDF)



#Final cleanup and setting clean_train.

MClean <- clean_train[-(86:91)]
MClean <- MClean[-(71:73)]
MClean <- MClean[-(60:69)]
MClean <- MClean[-(48:56)]
MClean <- MClean[-(5:25)]

# Cleaning the testing data, except "problem_id"
 
cTest <- evaluation_data[,-(1:7)]
Nnames[102] <- "problem_id" # to put problem_id 
cTest <- cTest[Nnames]
cTest <- cTest[-(86:91)]
cTest <- cTest[-(71:73)]
cTest <- cTest[-(60:69)]
cTest <- cTest[-(48:56)]

x=MClean
y=cTest[-(5:25)]

```
## Analysis And Predition

In this section is defined the random forest and the matrix to determine the answers. 

```{r}
set.seed(67) #(it can be any number)
rf <- foreach(ntree=rep(10, 5), .combine=randomForest::combine, .packages='randomForest') %dopar% {
  randomForest(x, y, ntree=ntree) 
}

predictions1 <- predict(rf, newdata=training)
confusionMatrix(predictions1,training$classe)

predictions2 <- predict(rf, newdata=testing)
confusionMatrix(predictions2,testing$classe)

```

## Answers
The following code, it was not created by me.

```{r}

pml_write_files = function(x){
  n = length(x)
  for(i in 1:n){
    filename = paste0("problem_id_",i,".txt")
    write.table(x[i],file=filename,quote=FALSE,row.names=FALSE,col.names=FALSE)
  }
}

x <- evaluation_data
x <- x[feature_set[feature_set!='classe']]
answers <- predict(rf, newdata=x)

pml_write_files(answers)

```
